For submission to the Journal of Integrated Pest Management

### 2021-04-02 ofv_fife_2021.Rmd
Made some final minor tweaks, should be ready for submission soon

---
title: "For submission to the Journal of Integrated Pest Management"
subtitle: "Category: 'Issues'"
output: 
  word_document:
    reference_docx: ../r-word-templates/word-template-jis.docx
# - html_document
bibliography: 'thesis.bib'
csl: 'j_med_entomol.csl'
#always_allow_html: true
---
```{r setup, include=FALSE}
#setup options
knitr::opts_chunk$set(fig.width=12, fig.height=8, echo=FALSE)

@@

The first report of OFV in the United States is thought to be @Ko1985, who describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.  The significance of this report is their reference to spoke-wheel configurations of the viral particles [@Ko1985], a sign typically associated with OFV infection [@Chang1976]. Unfortunately, @Ko1985 made no mention of mites or further investigations of this virus. The first certain report of OFV was from Hawaii in 2001 [@citation], while the first report from the continental US was by @Bratsch2015. In that publication, the authors confirmed the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis and its association with *Brevipalpus* mites [@Bratsch2015]. The authors did not make a conclusive species identification but suggested the mite vector was within the *B. californicus* group, as referred by @Kondo2003.

>>>>

---
title: "For submission to the Journal of Integrated Pest Management"
subtitle: "Category: 'Issues'"
output: 
  word_document:
    reference_docx: ../r-word-templates/word-template-jis.docx
# - html_document
bibliography: 'bib/thesis.bib'
csl: 'j_med_entomol.csl'
#always_allow_html: true
---
```{r setup, include=FALSE}
#setup options
knitr::opts_chunk$set(fig.width=12, fig.height=8, echo=FALSE)

@@

The first report of OFV in the United States is thought to be @Ko1985, who describes nuclear inclusions caused by an undescribed bacilliform rhabdovirus in *Brassia* orchids.  The significance of this report is their reference to spoke-wheel configurations of the viral particles [@Ko1985], a sign typically associated with OFV infection [@Chang1976]. Unfortunately, @Ko1985 made no mention of mites or further investigations of this virus. The first certain report of OFV was from Hawaii in 2001 [@Blanchfield2001], while the first report from the continental US was by @Bratsch2015. In that publication, the authors confirmed the presence of OFV in *Phalaenopsis* hybrids in the US, using TEM of ultrathin sections of plant tissue as well as molecular sequence analysis and its association with *Brevipalpus* mites [@Bratsch2015]. The authors did not make a conclusive species identification but suggested the mite vector was within the *B. californicus* group, as referred by @Kondo2003.
